### 2016-07-11 R/ITHIM.Rmd
First look at MET Key data

```{r vargo, echo = FALSE, eval = TRUE}
library(ggplot2)
library(reshape2)
library(plyr)

@@

metkey <- as.matrix(c(3.0,7.3,5.0,6.5,7.5,3.5,5.8,7.8,6.0,8.0,3.8,7.8,8.0,5.3,7.3,9.8,6.3,7.0,7.0,5.0,6.8,3.0,3.5,5.5,6.0,4.0,6.0,3.0,3.0,3.0), nrow = 1, ncol=30)
summary.2c <- mapply(`*`,summary.2b,metkey)
mets <- rowSums(summary.2c)
summary.2a$mets <- mets

@@

```{r figures, echo = FALSE, eval = TRUE}

@@

Note that `r round(100*sum(zeroMETs)/length(zeroMETs),1)`% of the
entries were zero minutes and the above densities are for non-zero
METs only.

```{r nonZeroMETsLogNormal, echo = FALSE, message = FALSE, eval = TRUE, warning = FALSE, error = TRUE}
parameters <- ddply(use[!zeroMETs,], .(sexcat, agecat2), summarise,
             mean_min = mean(minutes, na.rm=T),
             mean_mets = mean(mets, na.rm=T),
             sd_min = sd(minutes, na.rm=T),
             sd_mets = sd(mets, na.rm=T)
)
cv_mets <- with(parameters, sd_mets/mean_mets)
cv_min <- with(parameters, sd_min/mean_min)
cv0_mets<- mean(cv_mets)

@@

>>>>

```{r vargo, echo = FALSE, eval = FALSE}
library(ggplot2)
library(reshape2)
library(plyr)

@@

metkey <- as.matrix(c(3.0,7.3,5.0,6.5,7.5,3.5,5.8,7.8,6.0,8.0,3.8,7.8,8.0,5.3,7.3,9.8,6.3,7.0,7.0,5.0,6.8,3.0,3.5,5.5,6.0,4.0,6.0,3.0,3.0,3.0), nrow = 1, ncol=30)

summary.2c <- mapply(`*`,summary.2b,metkey)
mets <- rowSums(summary.2c)
summary.2a$mets <- mets

@@

```{r figures, echo = FALSE, message = FALSE, eval = FALSE, warning = FALSE, error = TRUE}

@@

<!--
     Note that `r round(100*sum(zeroMETs)/length(zeroMETs),1)`% of the
entries were zero minutes and the above densities are for non-zero
METs only.
-->

```{r nonZeroMETsLogNormal, echo = FALSE, message = FALSE, eval = FALSE, warning = FALSE, error = TRUE}
parameters <- ddply(use[!zeroMETs,], .(sexcat, agecat2), summarise,
             mean_min = mean(minutes, na.rm=T),
             mean_mets = mean(mets, na.rm=T),
             sd_min = sd(minutes, na.rm=T),
             sd_mets = sd(mets, na.rm=T)
)
cv_mets <- with(parameters, sd_mets/mean_mets)
cv_min <- with(parameters, sd_min/mean_min)
cv0_mets<- mean(cv_mets)

@@

```{r matrices, echo = FALSE, message = FALSE, eval = FALSE, warning = FALSE, error = TRUE}
nonTravelMETs <- rbind(0,rbind(0,cbind(parameters$mean_mets[7:12], parameters$mean_mets[1:6])))
nonTravelMETsNormalized <- nonTravelMETs/nonTravelMETs[3,2]
meanNonTravelMETs <- nonTravelMETs[3,2]

```{r plotMatrix, echo = FALSE, message = FALSE, eval = FALSE, warning = FALSE, error = TRUE}
D <- melt(nonTravelMETsNormalized)
ggplot(D, aes(Var2, value)) + geom_bar(aes(fill=Var1), stat = "identity", position = "dodge")
```

```{r fooFunction, echo = FALSE, message = FALSE, eval = FALSE, warning = FALSE, error = TRUE}
probActive <- 0.15
METQuintiles <- mapply(getMETQuintiles, nonTravelMETsNormalized*nonTravelMETs, MoreArgs = list(cv = cv0_mets, p = probActive, size = 1e4), SIMPLIFY = FALSE)
```

```{r newMETs}
newMETsFile <- "~/GHI/data/ATUS_to_METS_key.csv"
newMETs <- read.csv(file = newMETsFile, stringsAsFactors = FALSE, colClasses = c("character","character","character","character","numeric","character","character","character"))
dataColumns <- c(1,5)
D <- newMETs[,dataColumns]
metaData <- newMETs[,-dataColumns]
newMETs <- list(Data = D, metaData = metaData)
```

```{r readnewMETs}
summaryFile <- "~/GHI/data/atussum_0311.dat"
summary <- read.table(summaryFile, header=T, skip=0, sep=",")
metaDataColumns <- 1:24
summaryList <- list(Data = summary[,-metaDataColumns], metaData = summary[,metaDataColumns])
activities <- colnames(summaryList$Data)
metKey <- newMETs$Data$AinsworthMETS
activityCode <- ifelse(nchar(newMETs$Data$X6.digit.activity.code)==5,paste0("t0",newMETs$Data$X6.digit.activity.code),paste0("t",newMETs$Data$X6.digit.activity.code))
names(metKey) <- activityCode
activities[!(activities %in% names(metKey))]
names(metKey)[!(names(metKey) %in% activities)]
```

```{r metKey}
metKeyVector <- metKey[activities]/60*7
names(metKeyVector) <- activities
metKeyMatrix <- matrix(metKeyVector, nrow = nrow(summaryList$Data), ncol = length(metKeyVector), byrow = TRUE)
METs <- rowSums(summaryList$Data * metKeyMatrix, na.rm = TRUE)
hist(METs, breaks = 75)
```
